Novel genetic control of migratory diapause in Australian Monarch Butterflies

### 2022-04-22 paper/paper_draft.Rmd
more paper updates, reworked to not conclude which re-emergence hypothesis is correct and to focus on proximate vs facultative genes.

---
title: "Genetic Determinants of Migratory Behaviours in Australian Monarch Butterflies"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: "paper-files/style_ref.docx"
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    fig_width: 7
    fig_height: 6
bibliography: "paper-files/citations.bib"
csl: "paper-files/council-of-science-editors-author-date.csl"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}\doublespacing
  - \usepackage{sectsty}\sectionfont{\fontsize{12}{12}\selectfont}
  - \usepackage{sectsty}\subsectionfont{\normalfont\itshape\fontsize{12}{12}\selectfont}
  - \usepackage[round]{natbib}
indent: true
sansfont: Times New Roman
fontsize: 12pt
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(snpR); library(data.table); library(ggplot2); library(gridExtra); library(dplyr)

@@

Adaptation via a transition to residency is of both particular interest and concern for the conservation of migratory species. While switching to a resident life history can allow species to avoid the increasing risks of migration [and the intrinsically very energetic large costs of migration in general, see @McWilliams2004; @Rankin1992; @Wikelski2003], there is reasonable concern that the "extinction" of migration may not be easily reversible in some species.

This is, for example, a major concern for Monarch Butterflies (Danaus plexippus). North American migratory monarch populations have experienced severe declines over the last several decades, sparking a fear of what Semmens et al. [-@Semmens2016] called a "Quasi-extinction" of the migratory phenotype driven by changes in the selective forces acting on the species to favor resident individuals. Interestingly, however, there is at least one population of Monarchs in Australia that have apparently secondarily re-aquired migratory behavior after previously shifting to a resident life history. This population, which was established sometime before 1871, is the product of a series of sequential self-introductions that stepping-stoned across the Pacific ocean from North America beginning sometime in the early 1840s after the introduction of their host plants enabled individuals to survive after being blown from the mainland [@Zalucki2004]. Monarchs are not migratory on any Pacific islands, and no migratory behavior was observed until the 1930s, when non-reproductive overwintering aggregations were observed in northern New South Wales [NSW, see @James2019]. These and other individuals were later shown to migrate hundreds of kilometers each year to their wintering grounds from more southerly, inland locations in NSW [@James2019]. These populations, descended from over 50 years (or hundreds of generations) of non-migratory butterflies, were able to rapidly re-evolve a migratory life history. Understanding how they did so could provide crucial context around the "extinction" of migration in monarchs and other species.

There are three distinct possibilities for the re-evolution of migration in Australian monarchs: 1) monarchs maintained causal genetic variation associated with migration as they passed through repeated population bottlenecks during their Pacific expansion,  2) new mutations arose in Australian monarchs that enabled migration in those populations, or 3) individuals that moved (likely assisted by humans) from North America re-introduced the needed genetic variants for migration. Of these options, both one and two seem unlikely *a priori*, since they require either the unlikely chance retention of _both_ the migratory and non-migratory genetic variants across a long period of intense genetic drift (since both migratory and resident individuals are present in Australia) or the rapid acquisition of mutations associated with migration following their removal from the population, respectively. The third hypothesis also seems unlikely given the presumably low--but as of yet un-assessed--rate of artificial migration between Australia and North America.

To address these hypotheses, we studied continuously breeding monarch populations in Queensland (QLD). While these populations do not experience substantial seasonal fluctuations in resources availability, and thus do not migrate [@James2019], recent work has shown that reproductive diapause can be induced in some, *but not all* individuals from these populations if they are exposed to a reduction in photoperiod during development [@Freedman2018]. In brief, reproductive diapause, where individuals delay their reproductive maturation, is a critical phenotype for migratory individuals because it allows them to invest more heavily in energy storage and increase their average longevity [@Herman2001]. Like other migratory behaviors, diapause is controlled by changes in day length, temperature, and other seasonal fluctuations [@Goehring2002].

@@

```{r import_and_diversity, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}
#==========prep data==========
# read in genotypes and metadata
sample.meta <- read.table("../data/sample_metadata.txt", header = T, stringsAsFactors = F)
genos <- read.table("../data/v4/genotypes.geno", stringsAsFactors = F)
snp.meta <- genos[,1:2]
genos <- genos[,-c(1:2)]
colnames(snp.meta) <- c("scaffold", "position")

@@

# Results
## Sequencing results

@@

Genetic diversity levels were extremely similar between our two years ($\pi =$ `r round(diversity$weighted_mean_pi[2], 3)` and `r `diversity$weighted_mean_pi[3]` and $H_{o}$ = `r round(diversity$weighted_mean_ho[2], 3)` and `r round(diversity$weighted_mean_ho[3], 3)` for 2016 and 2018, respectively). Each year had a slight heterozygote excess ($F_{IS}$ = `r round(diversity$weighted_mean_fis[2], 3)` and `r round(diversity$weighted_mean_fis[3],3)` for 2016 and 2018, respectively), although that excess was lower if all samples were considered jointly ($F_{IS}$ = `r round(diversity$weighted_mean_fis[1], 3)`). Pairwise $F_{ST}$ between the two years was small but marginally significant (`r round(fst$weighted_mean_fst[1], 3)`, $p =$ `r round(fst$weighted_mean_fst_p[1], 3)`. We found no significant differences between the two sample years on either the PCA or the NGSadmix results, with clustering instead driven by family (Figure 1).

@@

Diapuse status was strongly biased by Maternal Family (Fisher's Exact Test, $p$ = `r round(fisher_res$p.value)`, see Figure 2a). We identified one small region of chromosome 11 roughly between positions 5,589,278 to 5,619,459 containing many loci associated with diapause status well beyond the background level of association, including three SNPs from two different RAD-tags, that had a $p$-value  $\le 5 \times 10^{-5}$ (Figure 2b). This region overlaps the gene DPOGS208560, a protein modifying gene, and was still strongly associated with diapause if only the 2018 butterflies alone were examined. We also identified one locus with a $p$-value  $\le 5 \times 10^{-5}$ on chromosome 16, but there were no other significantly associated loci nearby.

@@

## Re-evolution of Diapaue Control in Australian Monarch Butterflies

@@

What is surprising, however, is that this gene has not been previously identified as a candidate migration gene in monarchs previously. Specifically, DPOGS208560 was not among the 536 genes located in regions of the genome found to be significantly associated with contrasts between migration and residency between North and South American, Pacific, and European populations by Zhan et al. [-@Zhan2014]. This suggests that in Australian monarchs, reproductive diapause re-evolved via selection acting on new mutations (hypothesis 2 above), not via the conservation of diapause alleles during the expansion of the species across the Pacific or via re-introduction from North America following the establishment of the population in Australia (hypotheses 1 and 3, respectively), since if either of the latter two hypotheses were correct, we should have observed that one of the previously identified genes was also associated with diapuase in Australia.

This leads to a natural question: are the other traits that, along with reproductive diapause, constitute the migratory syndrome in Australian monarchs also the result of novel mutations? While our study only examined associations with diapause, we suggest that it is probably unlikely that only one migratory trait re-evolved via new mutations, since any other causal alleles would still have either had to survive genetic bottlenecks (hypothesis 1) or be re-introduced (hypothesis 2), and if they *had* been re-introduced, it would be more likely to see *all* of the same migratory genes as observed in North American monarchs, since migrants would pass their entire migratory suite into the Australian population. Nonetheless, it is still possible that migratory genes in Australian monarchs are composed of a mosaic of two or more of these options, and future research on directed flight or other migratory traits is still needed to disentangle the evolution of migration in Australian Monarchs.

@@

Our work suggests that even if migration goes fully "quasi-extinct" in monarchs, it may not be lost forever. If we had found that diapause was controlled by ancestrally derived allelic variation (hypotheses 1 or 3), migration in monarchs would potentially not rapidly re-emerge following the fixation of residency if conditions were to change such that it migration was once again fit. Given that migration in Monarchs appears to be an ancestral condition shared with its sister taxa, *Danaus erippus*, this was a real concern, since the deeply shared ancestral migratory variance may have only evolved once and be unlikely to do so again. Our work, however, suggests that migration can rapidly re-evolve in monarch butterflies via new mutations, and so *might* be able to quickly re-appear if it is lost. At the very least, we can be assured that for monarchs in particular, migrants in Australia constitute a reservoir of migratory alleles that could be tapped for North America if needed.

It is difficult to say what these results entail for the conservation of migratory species as a whole. While monarchs may be able to quickly recover from the loss of migratory behavior should conditions improve, it is unlikely that this is the case for most other migratory species of conservation concern, particularly for vertebrates. For example, if we assume that monarchs have a generation time of approximately seven generations per year for continuous breeding, monarchs in Australia went through roughly ~ `r 7*50` generations in the 50 or so years since they were first reported on the continent. Although they likely experienced a strong bottleneck initially, they were probably at a relatively large effective size for most of that time. Taken together, monarchs would have had a large opportunity space for the generation of new migratory alleles. In contrast, take for example Chinook and steelhead salmon (*Oncorhynchus tshawytscha* and *mykiss*, respectively). Pre-mature migration, a migratory life history variant in both species where some portion of the population return to their natal streams earlier than others, seems to be controlled by a ancestrally derived (but independently evolved) allelic variant at the GREB1L gene, which has been lost from the majority of populations due to [@Princee1603198; @Thompson177]. Salmon have *much* longer generation times (several years in both species), and so we should not expect pre-mature migration to quickly re-evolve in salmon as did migration in monarchs.

Nonetheless, our findings are still optimistic for the future of migration in monarch butterflies and other insects.

@@

This study suggests that reproductive diapause in Australian monarch butterflies was re-evolved via novel mutations rather than conserved as the species expanded across the Pacific. More research is needed to determine if the other migratory syndrome traits in Australian monarchs were re-evolved via new mutations as well, but this work nonetheless shows that monarchs are capable of rapidly re-evolving a migratory life-history after previously shifting to residency in the correct ecological context.

@@

flextable::regulartable(Tab1, cwidth = 1.2) %>% flextable::set_caption(., "Table 1: Counts of individuals per reproductive status in each year.")
```

```{r Figure_1_print,echo=FALSE,warning=FALSE,fig.cap="Principal Component Analysis of the monarchs from 2016 and 2018, colored by maternal family.",fig.width=8, fig.height=8, fig.align='center', fig.cap.style="Image Caption"}

>>>>

---
title: "Novel genetic control of migratory diapause in Australian Monarch Butterflies"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    reference_docx: "paper-files/style_ref.docx"
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    fig_width: 7
    fig_height: 6
bibliography: "paper-files/citations.bib"
csl: "paper-files/council-of-science-editors-author-date.csl"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}\doublespacing
  - \usepackage{sectsty}\sectionfont{\fontsize{12}{12}\selectfont}
  - \usepackage{sectsty}\subsectionfont{\normalfont\itshape\fontsize{12}{12}\selectfont}
  - \usepackage[round]{natbib}
indent: true
sansfont: Times New Roman
fontsize: 12pt
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(snpR); library(data.table); library(ggplot2); library(gridExtra); library(dplyr); library(openxlsx); library(lme4)

@@

Adaptation via a transition to residency is of both particular interest and concern for the conservation of migratory species. While switching to a resident life history can allow species to avoid the increasing risks of migration [and the intrinsically very energetic large costs of migration in general, see @McWilliams2004; @Rankin1992; @Wikelski2003], there is reasonable concern that the "extinction" of migration may not be easily reversible in some species. This is concerning since migratory life-history variation is expected to increase population adaptability [@Pulido2007], and thus the permanent loss of migration could potentially compromise the long term population persistence.

This is, for example, a major concern for Monarch Butterflies (Danaus plexippus). North American migratory monarch populations have experienced severe declines over the last several decades, sparking a fear of what Semmens et al. [-@Semmens2016] called a "Quasi-extinction" of the migratory phenotype driven by changes in the selective forces acting on the species to favor resident individuals. In addition to the damage to the long-term population persistence that could result from the loss of migration in North American, the annual monarch migration is publicly-beloved and its loss would be culturally costly [@Gustafsson2015].

Interestingly, however, there is at least one population of Monarchs in Australia in which migratory behavior has re-emerged after previously shifting to a resident life history. This population, which was established sometime before 1871, is the product of a series of sequential self-introductions that stepping-stoned across the Pacific ocean from North America beginning sometime in the early 1840s after the introduction of their host plants enabled individuals to survive after being blown from the mainland [@Zalucki2004]. Monarchs are not migratory on any Pacific islands, and no migratory behavior was observed until the 1930s, when non-reproductive overwintering aggregations were observed in northern New South Wales [NSW, see @James2019]. These and other individuals were later shown to migrate hundreds of kilometers each year to their wintering grounds from more southerly, inland locations in NSW [@James2019]. After over 50 years (or hundreds of generations) without migration, a migratory life-history re-emerged in these populations. Understanding how this happened could provide crucial context around the "extinction" of migration in monarchs and other species.

To better understand how migration re-emerged in Australian monarchs, we studied continuously breeding monarch populations in Queensland (QLD). While these populations do not experience substantial seasonal fluctuations in resources availability, and thus do not migrate [@James2019], recent work has shown that reproductive diapause can be induced in some, *but not all* individuals from these populations if they are exposed to a reduction in photoperiod during development [@Freedman2018]. In brief, reproductive diapause, where individuals delay their reproductive maturation, is a critical phenotype for migratory individuals because it allows them to invest more heavily in energy storage and increase their average longevity [@Herman2001]. Like other migratory behaviors, diapause is controlled by changes in day length, temperature, and other seasonal fluctuations [@Goehring2002].

@@

```{r import_and_diversity, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}
# L <- # total number of sequenced bases

#==========prep data==========
# read in genotypes and metadata
sample.meta <- read.table("../data/sample_metadata.txt", header = T, stringsAsFactors = F)
genos <- read.table("../data/v4/genotypes.geno", stringsAsFactors = F)
snp.meta <- genos[,1:2]
genos <- genos[,-c(1:2)]
colnames(snp.meta) <- c("scaffold", "position")

@@

```{r re_analyze, include=FALSE}
old_phenotypic <- read.xlsx("../data/monarch_development.xlsx")

mod_AsRa <- lme(Aspect_Ratio ~ Yolked_Oocytes, random = ~ 1|Female_Line, old_phenotypic, na.action = na.omit)
mod_Area <- lme(Marea ~ Yolked_Oocytes, random = ~ 1|Female_Line, old_phenotypic, na.action = na.omit)

We also briefly re-analyzed phenotypic data from the same earlier study that provided our 2016 monarch studies [@Freedman2018] in order to determine if wing shape or size was correlated with reproductive diapause by fitting a linear mixed effect model with wing shape or size as response variables against the number of yolked oocytes as a fixed effect and maternal family as a random effect using the R package nnlme [@Pinheiro2007].

# Results
## Sequencing results
We sequenced a total of 417,846,352 reads across all individuals, 98.8% of which mapped to the monarch reference genome. 244,443,414 reads were maintained after filtering (1,158,500 per sample, on average), encompassing X total sequenced bases. From this, we called `r prettyNum(nsnps(dat),big.mark=",",scientific=FALSE)` individual SNPs following filtering.

@@

Genetic diversity levels were extremely similar between our two years ($\pi =$ `r round(diversity$weighted_mean_pi[2], 3)` and `r diversity$weighted_mean_pi[3]` and $H_{o}$ = `r round(diversity$weighted_mean_ho[2], 3)` and `r round(diversity$weighted_mean_ho[3], 3)` for 2016 and 2018, respectively). Each year had a slight heterozygote excess ($F_{IS}$ = `r round(diversity$weighted_mean_fis[2], 3)` and `r round(diversity$weighted_mean_fis[3],3)` for 2016 and 2018, respectively), although that excess was lower if all samples were considered jointly ($F_{IS}$ = `r round(diversity$weighted_mean_fis[1], 3)`). Pairwise $F_{ST}$ between the two years was small but marginally significant (`r round(fst$weighted_mean_fst[1], 3)`, $p =$ `r round(fst$weighted_mean_fst_p[1], 3)`. We found no significant differences between the two sample years on either the PCA or the NGSadmix results, with clustering instead driven by family (Figure 1).

@@

Diapuse status was strongly biased by Maternal Family (Fisher's Exact Test, $p$ = `r round(fisher_res$p.value)`, see Figure 2a). We identified one small region of chromosome 11 roughly between positions 5,589,278 to 5,619,459 containing many loci associated with diapause status well beyond the background level of association, including three SNPs from two different RAD-tags that had a $p$-value  $\le 5 \times 10^{-5}$ (Figure 2b). This region overlaps the gene DPOGS208560, a protein modifying gene, and was still strongly associated with diapause if only the 2018 butterflies alone were examined. We also identified one locus with a $p$-value  $\le 5 \times 10^{-5}$ on chromosome 16, but there were no other significantly associated loci nearby.

We found that wing shape was significantly negatively correlated with the number of yolked oocytes in Freedman et al.'s [-@Freedman2018] earlier study ($p$ = `r round(summary(mod_AsRa)$tTable[2,5], 3)`) after accounting for maternal family. Wing size was also negatively correlated with the number of yolked oocytes, but not significantly so after accounting for maternal family ($p$ = `r round(summary(mod_Area)$tTable[2,5], 3)`.

@@

## Re-emergence of Diapaue Control in Australian Monarch Butterflies

@@

What is surprising, however, is that this gene has not been previously identified as a candidate migration gene in monarchs previously. Specifically, DPOGS208560 was not among the 536 genes located in regions of the genome found to be significantly associated with contrasts between migration and residency between North and South American, Pacific, and European populations by Zhan et al. [-@Zhan2014]. There are two distinct possibilities for that could explain the origin of this gene variant: the DPOGS208560 variant we observed is either present in North America but was not previously recognized as associated with migration or is the result of a new mutation which occurred in Australian monarchs. In the former case, this allele was either maintained as monarchs passed through repeated population bottlenecks during their Pacific expansion or was secondarily re-introduced by immigrant individuals from North America (which would have likely been anthropogenic in origin).

Since we *only* observed that only the DPOGS208560 gene was associated with diapause in Australian monarchs, it seems unlikely that secondary reintroduction of migratory monarch butterflies from North America could explain the re-emergence of migratory behavior in Australia, since there would be no reason for other *known* migratory associated genes to have not also made the jump back across the pacific. Since the SNP loci that we located are not perfectly associated with diapause and are thus likely to only be in linkage with any causal variation rather than the causal variants themselves, our work cannot currently delineate between the other two options (maintenance of variance at DPOGS208560 during the pacific crossing or a new mutation). If the actual causal loci were to be identified, it would then be possible to determine which gene versions are present in North America or across the Pacific and thus determine the origin of the DPOGS208560 diapause variant in Australia.

## Proximate vs Facultative Migratory Alleles

Regardless, however, if it is interesting that DPOGS208560 had not been previously noted as associated with migration in monarch butterflies. In their 2014 study, Zhan et al. generally focused their discussion of migratory genetics on Collagen IV $\alpha$-1, one of three genes they found that were strong outliers for association with migration. This gene is involved in muscle functioning in insects [@Schnorrer2010], and Zhan et al hypothesized that divergence at this gene was driven by selection for increased wing strength and muscle efficiency to facilitate long-distance migration. While they mentioned that the remaining significantly associated genes were enriched for the "morphogenesis, neurogenesis, and extracellular matrix/basement membrane" functional terms, they were not otherwise discussed (DPOGS208560 does not have any of these functional terms). Note that it is entirely possible that DPOGS208560 also contributes to diapause and migration in butterflies outside of Australia, but that the quantitative effect of other genes (a product of the effect sizes of the migratory alleles and their frequencies) dwarfs that of DPOGS208560, thus concealing the relative impact of the latter gene.

Regardless, as mentioned above, we did not identify loci near the Collagen IV $\alpha$-1 gene as associated with diapause. This is surprising, since although monarchs in Australia (like other non-migratory populations), have substantially smaller and shorter wings than their migratory counterparts [@Freedman2020], we also found from re-analyzing data from Freedman et al.'s 2018 study, wing shape is significantly correlated with reproductive development in Australian monarchs, which in implies that wing morphology is still a part of the correlated migratory syndrome in Australian monarchs.

However, it does make some sense that Collagen IV $\alpha$-1 would not be a key gene in populations that are *newly* migratory. We would argue that migratory genes can be divided into two basic categories: facultative migratory genes and those that are the proximate drivers of migratory behavior. Collagen IV $\alpha$-1 is, for example, a "facultative" migratory gene in that selection acting on it would serve to make already migratory individuals more fit, but would not itself *cause* or *enable* migratory behavior. DPOGS208560, on the other hand, is likely a proximate migratory gene, since diapause is *required* for migration because individuals that do not delay their reproductive investment have much shorter life-spans and cannot complete migration [@Herman2001]. Genes that control orientation, navigation, and directed flight would also fall into this category to varying extents. Any population that is newly migratory must have some proximate causal gene migratory variants or they would not display migratory behavior in the first place, but may only acquire facultative migratory gene variants over time as selection favors migratory individuals that are better able to complete their migration. That we found DPOGS208560 but not Collagen IV $\alpha$-1 to be associated with migration in Australia supports this hypothesis, and generally supports a complex interpretation of the genetic control of migration in monarchs.

@@

Our work suggests that even if migration goes fully "quasi-extinct" in monarchs, it may not be lost forever. Despite the loss of allelic variance during the successive bottlenecks, monarch butterflies either maintained the genetic variation needed to migrate or secondarily re-aquired it via mutation. This gives us some hope that the contemporary loss of migration that we have observed in many migrants may be reversible. At the very least, we can be assured that for monarchs in particular, migrants in Australia constitute a reservoir of migratory alleles that could be tapped for North America if needed.

It is difficult to say what these results entail for the conservation of migratory species as a whole. While monarchs may be able to quickly recover from the loss of migratory behavior should conditions improve, it is unlikely that this is the case for most other migratory species of conservation concern, particularly for vertebrates. For example, if we assume the latter hypothesis (migratory variance in Australian monarchs is the result of a new mutation), it is clear that monarchs have had ample evolutionary opportunity to re-acquire migratory mutations: monarchs have a generation time of approximately seven generations per year if continuously breeding, which means that monarchs in Australia went through roughly ~ `r 7*50` generations in the 50 or so years since they were first reported on the continent, and although they likely experienced a strong bottleneck initially, they were probably at a relatively large effective size for most of that time. Taken together, monarchs would have had a large opportunity space for the generation of new migratory alleles.

Alternatively, it is safe to assume that if migratory variance in Australian monarchs was maintained from North America, it is clear that this would only have been possible because selection was not actively acting against that variance. This is actually quite likely: monarchs in the Pacific are not exposed to substantial annual changes in day length or average temperature, and thus do not receive their main migratory cues. Environmentally triggered migratory variation, therefore, is probably selectively nearly neutral [although more fixed migratory variance, such as wing morphology, was likely selected against, driving the observed, repeated decreases in wing size and length across newly non-migratory monarch populations, see @Freedman2020], and is therefore more likely to be maintained in non-migratory populations.

In contrast, take for example Chinook and steelhead salmon (*Oncorhynchus tshawytscha* and *mykiss*, respectively). Pre-mature migration, a migratory life history variant in both species where some portion of the population return to their natal streams earlier than others, seems to be controlled by a ancestrally derived (but independently evolved) allelic variant at the GREB1L gene, which has been lost from the majority of populations due to [@Princee1603198; @Thompson177]. Salmon have *much* longer generation times (several years in both species), and so we should not expect pre-mature migration to quickly re-evolve in salmon as did migration in monarchs, and the pre-mature migration phenotypes have been selected against due to dam construction and other anthropogenic influences [@Thompson177], meaning that GREB1L is unlikely to be selectively netural in most populations.

Nonetheless, our findings are still optimistic for the future of migration in monarch butterflies or wherever selection on migratory alleles is merely relaxed instead of shifting to be increasingly negative.

@@

This study suggests that reproductive diapause in Australian monarch butterflies is influenced by a novel genetic mechanism via the DPOGS208560 gene, and that the previously identified migratory genetic elements, such as Collagen IV $\alpha$-1, were not associated with diapause in those populations. More research is needed to determine if the migratory variant of this gene is the result of ancestral variation maintained from North America or a new mutation. Regardless, our work is consistent with the hypothesis that proximate genetic mechanisms for migration are more likely to quickly re-emerge during a transition to a migratory life history than facultative mechanisms.

@@

flextable::regulartable(Tab1, cwidth = 1.2) %>% flextable::set_caption(., "Counts of individuals per reproductive status in each year.")
```

```{r Figure_1_print,echo=FALSE,warning=FALSE,fig.cap="Figure 1: Principal Component Analysis of the monarchs from 2016 and 2018, colored by maternal family.",fig.width=8, fig.height=8, fig.align='center', fig.cap.style="Image Caption"}
